### 2018-02-11 results.tex
fixing size of figures for submission, added style package for submission
last changes before submission

As explained in the methodology, the first step is to carry out a clustering process on the dataset in order to properly label the samples according to the classes to be used in the decision tree algorithm. Figure \ref{fig:clusters} presents a sample of the results obtained after applying the constrained \kmeans{} method, including subspacing. Recall that there are a total of 550 subspaces. Figure \ref{fig:clusters} shows three examples for each one of the subspaces considered, that is, three for each one of the 2-, 3-, and 4-feature subspace analyses. However, since it is not practical or possible to present three- or higher-dimensional plots, we display the results from a two-dimensional perspective into the the subspaces by picking 2 metrics at a time. (Note that the only cases in which this is a direct view into the clustering results are the 2-feature analysis cases.)

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\columnwidth]{figures/pdf/figure-07}
	\caption{Number of data samples in each class (poor, fair, good, excellent) after conducting a multi-dimensional constrained \kmeans{} clustering process using subspace analysis for 2, 3, and 4 features (GOF metrics). The dashed-line bar indicates the number of samples in the excellent class after oversampling. The color version of this figure is available only in the electronic edition.}
	\label{fig:count-classes}
\end{figure}

@@

Notice that almost independently of the tree (T3 being the exception), the metrics C4 (total energy) and C8 (response spectra) are consistently the most relevant ones in the decision algorithms. They are followed by C5 (peak acceleration) and C6 (peak velocity). On the other end, notice that C11 (strong phase duration) plays no role whatsoever in any of the trees, and that C1 (Arias integral), C2 (energy integral), and C3 (Arias intensity) have only small to marginal participations. The remaining metrics---C7 (peak displacement), C9 (Fourier spectrum), and C10 (Cross correlation)---have a somewhat significant participation, but only in the more complex trees.

>>>>

As explained in the methodology, the first step is to carry out a clustering process on the dataset in order to properly label the samples according to the classes to be used in the decision tree algorithm. Figure \ref{fig:clusters} presents a sample of the results obtained after applying the constrained \kmeans{} method, including subspacing. Recall that there are a total of 550 subspaces. Figure \ref{fig:clusters} shows three examples for each one of the subspaces considered, that is, three for each one of the 2-, 3-, and 4-feature subspace analyses. However, since it is not practical or possible to present three- or higher-dimensional plots, we display the results from a two-dimensional perspective into the subspaces by picking 2 metrics at a time. (Note that the only cases in which this is a direct view into the clustering results are the 2-feature analysis cases.)

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/pdf/figure-07}
	\caption{Number of data samples in each class (poor, fair, good, excellent) after conducting a multi-dimensional constrained \kmeans{} clustering process using subspace analysis for 2, 3, and 4 features (GOF metrics). The dashed-line bar indicates the number of samples in the excellent class after oversampling. The color version of this figure is available only in the electronic edition.}
	\label{fig:count-classes}
\end{figure}

@@

Notice that in all trees the metrics C4 (total energy) and C8 (response spectra) are consistently the most relevant ones in the decision algorithms. They are followed by C5 (peak acceleration) and C6 (peak velocity). On the other end, notice that C11 (strong phase duration) plays no role whatsoever in any of the trees, and that C1 (Arias integral), C2 (energy integral), and C3 (Arias intensity) have only small to marginal participations. The remaining metrics---C7 (peak displacement), C9 (Fourier spectrum), and C10 (Cross correlation)---have a somewhat significant participation, but only in the more complex trees.

### 2018-02-11 testing.tex
finished first complete version
last changes before submission

\begin{figure*}%[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-10}
	\caption{Results obtained using the validation algorithm of the selected decision tree T1 on the 2008 Chinno Hills earthquake simulation results reported by \citet{Taborda_2014_BSSA}. Here, the validation process is carried out separately for each component of motion (EW, NS, UD), for three different simulations corresponding to simulations done using the souther California velocity models: CVM-S, CVM-H, CVM-H+GTL. The contours maps are drawn for illustration purposes only based on the spatial distribution of the GOF validation class assigned to each station. The bottom histograms show the count of stations in each validation class. Stations are indicated with dots, and the epicenter with a Star. The color version of this figure is available only in the electronic edition.}
	\label{fig:res-gof-maps}
\end{figure*}

>>>>

\begin{figure*}%[th!]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-10}
	\caption{Results obtained using the validation algorithm of the selected decision tree T1 on the 2008 Chino Hills earthquake simulation results reported by \citet{Taborda_2014_BSSA}. Here, the validation process is carried out separately for each component of motion (EW, NS, UD), for three different simulations corresponding to simulations done using the southern California velocity models: CVM-S, CVM-H, CVM-H+GTL. The contours maps are drawn for illustration purposes only based on the spatial distribution of the GOF validation class assigned to each station. The bottom histograms show the count of stations in each validation class. Stations are indicated with dots, and the epicenter with a Star. The color version of this figure is available only in the electronic edition.}
	\label{fig:res-gof-maps}
\end{figure*}
